Reviewer comments from PeerJ

### 2015-02-06 PeerJComments.tex
jri edits to reviews

3) Fig. 1 should indicate the boundaries of the Mexican states that are used in describing population locations in the text (Jalisco, Colima, etc.). The four focal populations from Jalisco state should also be labeled in this figure (i.e., San Lorenzo, La Mesa, Ejutla A, Ejutla B).\\
\lev{I think this would make figure super busy and it's already verging on super busy. Maybe compromise on labelling the four pops within their pie charts.} 
\mbh{if you still have access to the figure in ArcGIS, should be easy to add state boundaries and you can make the boundaries very light to limit busyness; if not, I'd just label the Jalisco pies}

@@

\lev{Maybe in the text I can clarify total bands for individuals. I.e. if an individual is Hop/Hop, it will have a total of two bands that are split between the two PCRs, whereas if you are a heterozygote you will have 3 split between two PCRs. I wonder if we should ditch this figure entirely and I can draw up a cartoon one?}
\mbh{since reviewer 2 is also concerned about the PCR and this is the only thing the editor really mentioned, I think we need to be pretty thorough here.  Ideally we would have a Hop/Hop homozygote, a Hop/No Hop heterozygote, and a No Hop/No Hop homozygote in the figure.  We don't need the Pif since this really isn't mentioned in the manuscript.  Do you have gel figures showing both homozygotes and the heterozygote banding patterns? I'm afraid a cartoon would send the message that we don't have clear PCR results}

@@

8) Line 150. Why were only 100 bootstrap replicates used for the NJ analysis? 1000 is more typical.\\
\lev{I do not know the answer to this. I don't think that 1000 bootstraps would give us really a difference.}
\mbh{if you still have the input file for this analysis, should be a quick fix and show we're doing everything we can to address reviewer concerns}

@@

\mbh{We don't and it's kind of a strange/silly request...Jeff and I will deal with this}

@@

\mbh{my vote would be to remove the comparisons between \emph{parv} and \emph{mex} but to still note the high frequency in Jalisco}

@@

\mbh{Jeff and I will address this}

@@

\mbh{I might mention something briefly about \emph{parviglumis} being a ruderal species that can occur at high density (cite my \emph{Molecular Ecology} manuscript), but, no, I would not add a whole paragraph on the ecologies of the teosintes.}

@@

\mbh{we need to check this.  can you go back through emails or to your lab notebook to find whether this was sequenced?}

>>>>

3) Fig. 1 should indicate the boundaries of the Mexican states that are used in describing population locations in the text (Jalisco, Colima, etc.). The four focal populations from Jalisco state should also be labeled in this figure (i.e., San Lorenzo, La Mesa, Ejutla A, Ejutla B).\\
\lev{I think this would make figure super busy and it's already verging on super busy. Maybe compromise on labelling the four pops within their pie charts.} 
\mbh{if you still have access to the figure in ArcGIS, should be easy to add state boundaries and you can make the boundaries very light to limit busyness; if not, I'd just label the Jalisco pies}
\jri{raster in R is not too hard either.}

@@

\lev{Maybe in the text I can clarify total bands for individuals. I.e. if an individual is Hop/Hop, it will have a total of two bands that are split between the two PCRs, whereas if you are a heterozygote you will have 3 split between two PCRs. I wonder if we should ditch this figure entirely and I can draw up a cartoon one?}
\mbh{since reviewer 2 is also concerned about the PCR and this is the only thing the editor really mentioned, I think we need to be pretty thorough here.  Ideally we would have a Hop/Hop homozygote, a Hop/No Hop heterozygote, and a No Hop/No Hop homozygote in the figure.  We don't need the Pif since this really isn't mentioned in the manuscript.  Do you have gel figures showing both homozygotes and the heterozygote banding patterns? I'm afraid a cartoon would send the message that we don't have clear PCR results}
\jri{agree with the huff}

@@

8) Line 150. Why were only 100 bootstrap replicates used for the NJ analysis? 1000 is more typical.\\
\lev{I do not know the answer to this. I don't think that 1000 bootstraps would give us really a difference.}
\mbh{if you still have the input file for this analysis, should be a quick fix and show we're doing everything we can to address reviewer concerns}
\jri{agreed, should be easy to redo. while agree this is silly and i don't think 1000 will change anything, but since it's easy to do it's hard to argue against doing it.}

@@

\mbh{We don't and it's kind of a strange/silly request...Jeff and I will deal with this}
\jri{ i can do the simple but dumb calculation if you guys want for response to reviewers, but disagree we should include in manuscript. we mention they are at the tail of the empirical distribution from wright et al don't we?}

@@

\mbh{my vote would be to remove the comparisons between \emph{parv} and \emph{mex} but to still note the high frequency in Jalisco}
\jri{ok either way here}

@@

\mbh{Jeff and I will address this}
\jri{sloppy my ass. <censored> reviewer!}

@@

\mbh{I might mention something briefly about \emph{parviglumis} being a ruderal species that can occur at high density (cite my \emph{Molecular Ecology} manuscript), but, no, I would not add a whole paragraph on the ecologies of the teosintes.}
\jri{this sounds OK. a wee bit of self-citation there hufford?}

@@

\mbh{we need to check this.  can you go back through emails or to your lab notebook to find whether this was sequenced?}
\jri{i don't remember ever checking this. we checked the pif by PCRing stuff John had already sequenced in which i identified the pif}
